Temporal Activity Detection in Untrimmed Videos with Recurrent Neural Networks

### 2016-10-15 paper.tex
New figure

\begin{figure}[h]
\centering
\begin{subfigure}[b]{.5\textwidth}
    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_1}
    \texttt{Video ID: ArzhjEk4j\_Y \\
    Ground Truth: Building sandcastles \\
    \\
    Prediction: \\
    0.7896	Building sandcastles \\
    0.0073	Doing motocross \\
    0.0049	Beach soccer \\}
\end{subfigure}%
\begin{subfigure}[b]{.5\textwidth}
    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_4}
    \texttt{Video ID: VrNHEv6aR38 \\
    Ground Truth: Playing water polo \\
    \\
    Prediction: \\
    0.7645	Playing water polo \\
    0.2018	Swimming \\
    0.0065	Springboard diving\\}
\end{subfigure}

>>>>

\begin{figure}[h]
\centering
\begin{subfigure}[b]{.5\textwidth}
    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_1}
    \texttt{Video ID: ArzhjEk4j\_Y \\
    Ground Truth: Building sandcastles \\
    \\
    Prediction: \\
    0.7896	Building sandcastles \\
    0.0073	Doing motocross \\
    0.0049	Beach soccer \\}
\end{subfigure}%
\begin{subfigure}[b]{.5\textwidth}
    \includegraphics[width=0.9\linewidth]{img/results_visualization_classification_2}
    \texttt{Video ID: AimG8xzchfI \\
	Activity: Curling \\
    \\
    Prediction: \\
    0.3843	Shoveling snow \\
    0.1181	Ice fishing \\
    0.0633	Waterskiing \\}
\end{subfigure}
